Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-23 paper.tex
clean up and correct "clamping" description

Unfortunately, private keys have to be derived by hashing the seed and manipulating the bits.
RFC\-8032~\cite{RFC8032} specifies that of the 32-byte ``expanded'' private key:
\begin{itemize}[label=\textendash, itemsep=-0.5em]
\item Bits 0, 1, 2 are set to 0, ensuring that the key is a multiple of 8, thus avoiding small-subgroup attacks.
\item Bit 255 is set to 0, to ensure that the key is less than the order of the elliptic-curve group.
\item Bit 254 is to 1, to ensure that the Montgomery ladder computation used in scalar multiplication runs in constant time.
\end{itemize}
So, by definition, the key space for Ed25519 is non-linear.

>>>>

Unfortunately, private keys in Ed25519 have to be derived by hashing a private ``seed'' and manipulating the bits.
RFC\-8032~\cite{RFC8032} specifies that in the 32-byte private key:
\begin{itemize}[label=\textendash, itemsep=-0.5em]
\item Bits 0, 1, 2 are set to 0, ensuring that the key is a multiple of 8, thus avoiding small-subgroup attacks.
\item Bit 255 is set to 0, to ensure that the key is less than the order of the elliptic-curve group.
\item Bit 254 is set to 1, to ensure that the Montgomery ladder computation used in scalar multiplication runs in constant time.
\end{itemize}
So, by definition, the key space for Ed25519 is non-linear relative to the group order.
